openTSNE: a modular Python library for t-SNE dimensionality reduction and embedding

### 2020-12-15 paper/policar2020-opentsne.tex
Change tasic figure to 2x2 instead of 4x1
conclusion

@@

\begin{figure*}[htbp]
	\includegraphics[width=\textwidth]{tasic2018}
	\caption{\label{fig:tasic}
  We use \opentsne\ to create four different
	visualizations of the Tasic \textit{et al.}~\cite{tasic2018shared} data,
	each providing a different perspective into the topology of the data.
	The data set contains 21,874 single-cells originating from the mouse
	neocortex. Cluster annotations and colors are taken from the original
	publication. Warm colors correspond to excitatory neurons, cool colors
	correspond to inhibitory neurons, and gray/brown colors correspond to
	non-neuronal cells. Standard t-SNE \textbf{(a)} emphasizes local
	structure while increasing perplexity \textbf{(b)} results in a more
	meaningful layout of the clusters. We can also combine the two
	perplexities by using a multiscale kernel affinity model \textbf{(c)}
	and obtain a trade-off between global and local structure.
	Alternatively, we can inspect more fine-grained structure and reveal
  smaller clusters by using a more heavy-tailed kernel \textbf{(d)}.}
\end{figure*}

@@

\section*{Conclusion}
Text for this section \ldots

\fontsize{8}{10}\selectfont
\section*{Methods}

@@

\section*{Author's contributions}
P.G.P. implemented and maintains \opentsne library. M.S. helped in development
of mathematical foundations and advised on inclusion of the extensions.
B.Z. initiated and supervised the project. All three co-authors wrote
the manuscript.

>>>>

\renewcommand{\baselinestretch}{1.2}

@@

\begin{figure*}[htbp]
  \center
  \includegraphics[width=0.75\textwidth]{tasic2018}
	\caption{\label{fig:tasic}
  We use \opentsne\ to create four different
	visualizations of the Tasic \textit{et al.}~\cite{tasic2018shared} data,
	each providing a different perspective into the topology of the data.
	The data set contains 21,874 single-cells originating from the mouse
	neocortex. Cluster annotations and colors are taken from the original
	publication. Warm colors correspond to excitatory neurons, cool colors
	correspond to inhibitory neurons, and gray/brown colors correspond to
	non-neuronal cells. Standard t-SNE \textbf{(a)} emphasizes local
	structure while increasing perplexity \textbf{(b)} results in a more
	meaningful layout of the clusters. We can also combine the two
	perplexities by using a multiscale kernel affinity model \textbf{(c)}
	and obtain a trade-off between global and local structure.
	Alternatively, we can inspect more fine-grained structure and reveal
  smaller clusters by using a more heavy-tailed kernel \textbf{(d)}.}
\end{figure*}

@@

\section*{Conclusion}

Data visualization for efficient exploration and effective communication is integral to scientific progress~\cite{wong2012points}. It is of no surprise, then, that a technique called t-SNE that can embed multi-dimensional data within two-dimensional maps has gained such popularity. The t-SNE visualizations appear in numerous recent publications, including those in this journal, and are, in particular, instrumental for the advancement in specific fields of biology, such as single-cell transcriptomics. Yet, with growing data volume and the need for data integration from various experiments, the original t-SNE exhibits lack of scalability and susceptibility to batch effects. We here introduce \opentsne\, an open-source Python t-SNE library that addresses these concerns and includes recent methodological advancements. \opentsne\ can scale to millions of data records and fit local cluster exploration and global structure discovery. It is also the only existing t-SNE library that enables transfer learning in a principled manner, where new data can be embedded into existing atlases.

\section*{Author's contributions}
P.G.P. implemented and maintains \opentsne\ library. M.S. helped in the development of mathematical foundations and advised on the inclusion of the extensions. B.Z. initiated and supervised the project. All three co-authors wrote the manuscript.

\eject
\fontsize{8}{10}\selectfont
\section*{Online Methods}

@@
